{{< var titll >}}

### 2024-08-17 analyzer.qmd
all

## Install

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
data(package='ManifoldDestinyWASMD')
```

## Select case

```{webr-r}
dfl <- ManifoldDestinyWASMD::yout
```

## Counting

```{webr-r}
Countingprocess(dfl)
```

## Estimation

>>>>

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
#ls(package:ManifoldDestinyWASMP)
#data(package='ManifoldDestinyWASMD')
apps <- appn0
```

```{webr-r}
adat <- apps[[1]]
amet <- apps[[2]]
cob <- Countinggraphs(adat)
cob$purging(z=0) 
def <- Estimation(cob$rdfce)
```

```{webr-r}
def$regression("alpha=k0 + k1*g + k2*h")
summary(def$regsum[[1]])
```

```{webr-r}
def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
summary(def$regsum[[1]])
```
